Stack Safety as a Security Property

### 2021-04-01 tex/example1.tex
Extended examples a bit more

%\newcounter{pcctr}
%\setcounter{pcctr}{0}
%  \thepcctr & \stepcounter{pcctr} #1 & #2 & #3 & \text{#4}\\
%\newcommand*{\row}[4]{
%  \thepcctr & \stepcounter{pcctr} #2 & #3 & \text{#4}\\
%}
%\newcommand*{\tracerow}[5]{
%  #1 & #2 & #3 & #4 & \text{#5}\\
%}
%\newcommand*{\summary}[6]{
%\[
%\begin{array}{cccccc}
%  \PCname = #1 & r_0 = #2 & \rra = #3 & \rsp = #4 & r_4 = #5 & r_5 = #6
%\end{array}
%\]
%}
\newcommand{\negate}{\textrm{-}}

@@

\newcommand{\instrc}{lgray}
\newcommand{\mainsealc}{cyan}
\newcommand{\fsealc}{green}
\newcommand{\unsealc}{gray}
\newcommand{\emptyoutc}{white} % or gray for consistency with unusedc ?
\newcommand{\fulloutc}{white}

@@

int f(int z) {
10:     print z;
11[R]:  return (z+z);
}
\end{verbatim}
\caption{A Simple Call}
\label{fig:simple-program}
\end{subfigure}
\begin{subfigure}{.4\textwidth}  
\begin{center}
\begin{tabular}{l l}
{\tt 0} &
\memoryaddrs{4em}
\memory{2}{\unsealc}[{\makebox[0pt]{Unsealed}}]
~$\cdots$
\\
{\tt 1} &
\memoryaddrs{12em}
\memory{3}{\unsealc}
~$\cdots$
\MemoryLabel{-14em}{0.75em}{42}
\MemoryLabel{-10em}{0.75em}{0}
\vspace{.5em}
\\
{\tt 10} &
\memoryaddrs{12em}
\memory{2}{\mainsealc}[{\makebox[0pt]{Sealed(0)}}]%
\memory{1}{\unsealc}
~$\cdots$
\\
{\tt 2} &
\memoryaddrs{12em}
\memory{3}{\unsealc}
~$\cdots$
\MemoryLabel{-14em}{0.75em}{42}
\MemoryLabel{-10em}{0.75em}{0}
\\
\end{tabular}
\end{center}

@@

\begin{subfigure}{.35\textwidth}
\begin{verbatim}
int main() {
0:     int x = 42, y = 0;
1[C]:  y = f();
2:     print (x + y);
}

int f() {
10:     int z = *($SP-1);
11[R]:  return (z+z);
}
\end{verbatim}
\caption{A Confidentiality Violation}
\label{fig:conf1-program}
\end{subfigure}
\begin{subfigure}{.5\textwidth}  
\begin{center}
\begin{tabular}{l l l l}
{\tt 0} &
\memoryaddrs{4em}
\memory{3}{\unsealc}
~$\cdots$
\MemoryLabel{-14em}{0.75em}{a}
\MemoryLabel{-10em}{0.75em}{b}
\MemoryLabel{-7em}{0.75em}{c}
\vspace{.5em}
& &
\\
{\tt 1} &
\memoryaddrs{12em}
\memory{3}{\unsealc}
~$\cdots$
\MemoryLabel{-14em}{0.75em}{42}
\MemoryLabel{-10em}{0.75em}{0}
\MemoryLabel{-7em}{0.75em}{c}
\vspace{.5em} & &
\\
{\tt 10} &
\memoryaddrs{12em}
\memory{2}{\mainsealc}
\memory{1}{\unsealc}
~$\cdots$
\MemoryLabel{-14em}{0.75em}{42}
\MemoryLabel{-10em}{0.75em}{0}
\MemoryLabel{-7em}{0.75em}{c} &
\memoryaddrs{12em}
\memory{2}{\mainsealc}
\memory{1}{\unsealc}
~$\cdots$
\MemoryLabel{-14em}{0.75em}{a'}
\MemoryLabel{-10em}{0.75em}{b'}
\MemoryLabel{-7em}{0.75em}{c'}
\\
{\tt 11} &
\memoryaddrs{16em}
\memory{2}{\mainsealc}
\memory{1}{\unsealc}
~$\cdots$
\MemoryLabel{-14em}{0.75em}{42}
\MemoryLabel{-10em}{0.75em}{0}
\MemoryLabel{-7em}{0.75em}{0} &
\memoryaddrs{16em}
\memory{2}{\mainsealc}
\memory{1}{\unsealc}
~$\cdots$
\MemoryLabel{-14em}{0.75em}{a'}
\MemoryLabel{-10em}{0.75em}{b'}
\MemoryLabel{-7em}{0.75em}{b'}
\\
\end{tabular}
\end{center}

@@

\label{fig:conf1-trace}
\end{subfigure}
\end{figure}

@@

\begin{subfigure}{.35\textwidth}
\begin{verbatim}
int main() {
0[C]:  int t = f();
1[R]:  return;
}

@@

int g() {
20:     int z = *$SP;
21[R]:  return (z+z);
}
\end{verbatim}
\end{subfigure}
\begin{subfigure}{.5\textwidth}  
\begin{center}
\begin{tabular}{l l l l}
{\tt 13} &
\memoryaddrs{12em}
\memory{1}{\mainsealc}
\memory{3}{\unsealc}
~$\cdots$
\MemoryLabel{-18em}{0.75em}{a}
\MemoryLabel{-14em}{0.75em}{b}
\MemoryLabel{-10em}{0.75em}{5}
\MemoryLabel{-7em}{0.75em}{6}
\vspace{.5em}
& &
\\
{\tt 20} &
\memoryaddrs{12em}
\memory{1}{\mainsealc}
\memory{1}{\fsealc}
\memory{2}{\unsealc}
~$\cdots$
\MemoryLabel{-18em}{0.75em}{a}
\MemoryLabel{-14em}{0.75em}{b}
\MemoryLabel{-10em}{0.75em}{5}
\MemoryLabel{-7em}{0.75em}{6}
\vspace{.5em} &
\memoryaddrs{12em}
\memory{1}{\mainsealc}
\memory{1}{\fsealc}
\memory{2}{\unsealc}
~$\cdots$
\MemoryLabel{-18em}{0.75em}{a'}
\MemoryLabel{-14em}{0.75em}{b'}
\MemoryLabel{-10em}{0.75em}{c'}
\MemoryLabel{-7em}{0.75em}{d'}
\vspace{.5em}
&
\\
{\tt 21} &
\memoryaddrs{12em}
\memory{1}{\mainsealc}
\memory{1}{\fsealc}
\memory{2}{\unsealc}
~$\cdots$
\MemoryLabel{-18em}{0.75em}{a}
\MemoryLabel{-14em}{0.75em}{b}
\MemoryLabel{-10em}{0.75em}{5}
\MemoryLabel{-7em}{0.75em}{6}
\vspace{.5em} &
\memoryaddrs{12em}
\memory{1}{\mainsealc}
\memory{1}{\fsealc}
\memory{2}{\unsealc}
~$\cdots$
\MemoryLabel{-18em}{0.75em}{a'}
\MemoryLabel{-14em}{0.75em}{b'}
\MemoryLabel{-10em}{0.75em}{c'}
\MemoryLabel{-7em}{0.75em}{d'}
\vspace{.5em}
&
\\

@@

Two important details of confidentiality are reflected in figure \ref{fig:conf2}.

>>>>

\newcommand{\negate}{\textrm{-}}

@@

\newcommand{\mainsealc}{cyan}
\newcommand{\fsealc}{green}
\newcommand{\unsealc}{lgray}
\newcommand{\emptyoutc}{white} % or gray for consistency with unusedc ?
\newcommand{\fulloutc}{white}

@@

int f(int z) {
10:     print z;
11[R]:  return (z+z);
}
\end{verbatim}

\caption{A Simple Call}
\label{fig:simple-program}
\end{subfigure}
\begin{subfigure}{.4\textwidth}  
\begin{center}
\begin{tabular}{l l}
{\tt 0} &
\memoryaddrs{4em}
\memory{2}{\unsealc}[{\makebox[0pt]{Unsealed}}]
~$\cdots$
\\
{\tt 1} &
\memoryaddrs{12em}
\memory{3}{\unsealc}
~$\cdots$
\MemoryLabel{-14em}{0.75em}{42}
\MemoryLabel{-10em}{0.75em}{0}
\vspace{.5em}
\\
{\tt 10} &
\memoryaddrs{17em}
\memory{2}{\mainsealc}[{\makebox[0pt]{Sealed(0)}}]%
\memory{2}{\unsealc}
~$\cdots$
\MemoryLabel{-10em}{0.75em}{2}
\\
{\tt 2} &
\memoryaddrs{12em}
\memory{3}{\unsealc}
~$\cdots$
\MemoryLabel{-14em}{0.75em}{42}
\MemoryLabel{-10em}{0.75em}{0}
\MemoryLabel{-7em}{0.75em}{2}
\\
\end{tabular}
\end{center}

@@

\begin{subfigure}{.33\textwidth}
\begin{verbatim}
int main() {
0:     int x = 42, y = 0;
1[C]:  y = f();
2:     print (x + y);
}

int f() {
10:     int z = *($SP-1);
11[R]:  return (z+z);
}
\end{verbatim}
\label{fig:conf1-program}
\end{subfigure}
\begin{subfigure}{.59\textwidth}
\centering
\begin{tabular}{l l l}
  {\tt 0} &
  \multicolumn{2}{c}{
    \memoryaddrs{4em}
    \memory{3}{\unsealc}
    ~$\cdots$
    \MemoryLabel{-14em}{0.75em}{a}
    \MemoryLabel{-10em}{0.75em}{b}
    \MemoryLabel{-7em}{0.75em}{c}
    \vspace{.5em}
  } \\
  {\tt 1} &
  \multicolumn{2}{c}{
    \memoryaddrs{12em}
    \memory{3}{\unsealc}
    ~$\cdots$
    \MemoryLabel{-14em}{0.75em}{42}
    \MemoryLabel{-10em}{0.75em}{0}
    \MemoryLabel{-7em}{0.75em}{c}
    \vspace{.5em}
  } \\
  {\tt 10} &
  \memoryaddrs{20em}
  \memory{2}{\mainsealc}
  \memory{2}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-19em}{0.75em}{42}
  \MemoryLabel{-14em}{0.75em}{0}
  \MemoryLabel{-10em}{0.75em}{2}
  \MemoryLabel{-7em}{0.75em}{\bf d}
 &
  \memoryaddrs{20em}
  \memory{2}{\mainsealc}
  \memory{2}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-19em}{0.75em}{a'}
  \MemoryLabel{-14em}{0.75em}{b'}
  \MemoryLabel{-10em}{0.75em}{2}
  \MemoryLabel{-7em}{0.75em}{\bf d'}
  \\
  {\tt 11} &
  \memoryaddrs{20em}
  \memory{2}{\mainsealc}
  \memory{2}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-19em}{0.75em}{42}
  \MemoryLabel{-14em}{0.75em}{0}
  \MemoryLabel{-10em}{0.75em}{2}
  \MemoryLabel{-7em}{0.75em}{\bf 0}
  &
  \memoryaddrs{20em}
  \memory{2}{\mainsealc}
  \memory{2}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-19em}{0.75em}{a'}
  \MemoryLabel{-14em}{0.75em}{b'}
  \MemoryLabel{-10em}{0.75em}{2}
  \MemoryLabel{-7em}{0.75em}{\bf b'}
  \\
\end{tabular}

@@

\label{fig:conf1-trace}
\end{subfigure}
\caption{A Confidentiality Violation}
\end{figure}

@@

\begin{subfigure}{.32\textwidth}
\begin{verbatim}
int main() {
0[C]:  int t = f();
1[R]:  return;
}

@@

int g() {
20:     int z;
21[R]:  return (z+z);
}
\end{verbatim}
\end{subfigure}
\begin{subfigure}{.5\textwidth}  
\begin{center}
\begin{tabular}{l l l l}
{\tt 13} &
\memoryaddrs{12em}
\memory{1}{\mainsealc}
\memory{3}{\unsealc}
~$\cdots$
\MemoryLabel{-18em}{0.75em}{a}
\MemoryLabel{-14em}{0.75em}{b}
\MemoryLabel{-10em}{0.75em}{5}
\MemoryLabel{-7em}{0.75em}{6}
\vspace{.5em}
& &
\\
{\tt 20} &
\memoryaddrs{12em}
\memory{1}{\mainsealc}
\memory{1}{\fsealc}
\memory{2}{\unsealc}
~$\cdots$
\MemoryLabel{-18em}{0.75em}{a}
\MemoryLabel{-14em}{0.75em}{b}
\MemoryLabel{-10em}{0.75em}{5}
\MemoryLabel{-7em}{0.75em}{6}
\vspace{.5em} &
\memoryaddrs{12em}
\memory{1}{\mainsealc}
\memory{1}{\fsealc}
\memory{2}{\unsealc}
~$\cdots$
\MemoryLabel{-18em}{0.75em}{a'}
\MemoryLabel{-14em}{0.75em}{b'}
\MemoryLabel{-10em}{0.75em}{c'}
\MemoryLabel{-7em}{0.75em}{d'}
\vspace{.5em}
&
\\
{\tt 21} &
\memoryaddrs{12em}
\memory{1}{\mainsealc}
\memory{1}{\fsealc}
\memory{2}{\unsealc}
~$\cdots$
\MemoryLabel{-18em}{0.75em}{a}
\MemoryLabel{-14em}{0.75em}{b}
\MemoryLabel{-10em}{0.75em}{5}
\MemoryLabel{-7em}{0.75em}{6}
\vspace{.5em} &
\memoryaddrs{12em}
\memory{1}{\mainsealc}
\memory{1}{\fsealc}
\memory{2}{\unsealc}
~$\cdots$
\MemoryLabel{-18em}{0.75em}{a'}
\MemoryLabel{-14em}{0.75em}{b'}
\MemoryLabel{-10em}{0.75em}{c'}
\MemoryLabel{-7em}{0.75em}{d'}
\vspace{.5em}
&
\\

@@

Two important details of confidentiality are reflected in figure \ref{fig:conf2}.
First of all, it has multiple calls, and while we focus on the stack at the call
from line 13 to line 20, it should be clear that we also need to consider a similar
variant at the call from 0 to 10. Confidentiality is in this sense recursive: each
nested must obey confidentiality in its own right.

More importantly, careful readers will have noticed that the informal definition
of stack confidentiality refers to a variation of the entire stack, not just the
sealed portion. In fact, we support temporal stack safety, in which values left behind
by previous activations are also inaccessible. In this case, we connect temporal safety
firmly to the caller-callee attacker model -- {\tt f} stored some data in the variables
{\tt y} and {\tt z}, used it, then deallocated them by moving the stack pointer.
After the stack pointer is written over {\tt y}, the value of {\tt z} is still
left behind. Then {\tt g} can read it just by allocating and accessing an uninitialized
variable!

\paragraph*{Awkward Examples}
